Scheeper's Meager-NWD Game and the Menger Game

### 2014-05-14 phd/dissertation/_raw_chapter4.tex

\chapter{Locally Finite Games}

Results pertaining to the Locally Finite game related to the W games.

\section{basic results}

\begin{thm}
The following are equivalent for a locally compact space $X$:
    \begin{itemize}
    \item $X$ is paracompact
    \item $K \uparrow G_{K,L}(X)$.
    \end{itemize}
\end{thm}

However, often it is the presence of ``limited information'' strategies which can characterize interesting properties of a space.

\begin{defn}
A \textbf{limited information strategy} for a game is a function whose domain is restricted to less information than all previous moves by the opposing player.
\end{defn}

In the above mentioned paper, Gruenhage used the following limited information strategies to prove some interesting characterizations based on the game $G_{K,P}(X)$.

\begin{defn}
A \textbf{tactical strategy} considers only the most recent move by the opposing player. If Player $Z$ has a winning tactical strategy for a game $G$, this may be denoted $Z \uparrow_{\text{tact}} G$.
\end{defn}

\begin{defn}
A \textbf{Markov strategy} considers only the most recent move by the opposing player and the turn number. If Player $Z$ has a winning Markov strategy for a game $G$, this may be denoted $Z \uparrow_{\text{mark}} G$.
\end{defn}

\begin{thm}
The following are equivalent for a locally compact space $X$:
    \begin{itemize}
    \item $X$ is metacompact
    \item $K \uparrow_{\text{tact}}G_{K,P}(X)$.
    \end{itemize}
\end{thm}

\begin{thm}
The following are equivalent for a locally compact space $X$:
    \begin{itemize}
    \item $X$ is $\sigma$-metacompact
    \item $K \uparrow_{\text{mark}}G_{K,P}(X)$.
    \end{itemize}
\end{thm}

Upon learning these results, one might wonder the consequences of the existence of this type of limited information strategy:

\begin{defn}
A \textbf{predetermined strategy} considers only the turn number. If Player $Z$ has a winning predetermined strategy for a game $G$, this may be denoted $Z \prewin G$.
\end{defn}

Intuitively, if a player is using a predetermined strategy, then that player decides every move he or she will make before the game even begins, ignoring the other player's moves.

Consider the following trivial result:

\begin{defn}
A \textbf{button-mashing strategy} is a constant function. If Player $Z$ has a winning button-mashing strategy for a game $G$, this may be denoted $Z \uparrow_{\text{mash}} G$.
\end{defn}

\begin{prop}
The following are equivalent for any space $X$:
    \begin{itemize}
    \item $X$ is compact
    \item $K \uparrow_{\text{mash}}G_{K,P}(X)$.
    \end{itemize}
\end{prop}

Observing that giving $K$ the added information of turn number to a tactical strategy (making it Markov) changed the characterization of a metacompact space into a $\sigma$-metacompact space, it would be very convenient if adding that same information to a button-mashing strategy (making it predetermined) would similarly change the characterization of a compact space into $\sigma$-compact.

\begin{prop}
If $K \prewin G_{K,P}(X)$, then $X$ is $\sigma$-compact.
\end{prop}

\begin{proof}
Let $K_n$ be the sets given by the winning predetermined strategy. If they did not union to $X$, then the counter play $p_n=p$ for some $p\in X\setminus \bigcup_n K_n$ would defeat the ``winning'' strategy.
\end{proof}

\begin{thm}
If $Y$ is a locally compact, Lindel\"of space, then $K \prewin G_{K,P}(X)$.
\end{thm}

\begin{proof}
Let $\mathcal{K}$ be a collection of compact neighborhoods whose interiors cover $X$. By Lindel\"of, let $\{K_n : n<\omega\}$ be a countable subcollection whose interiors cover $X$. We then define the predetermined strategy $\sigma(n)=\bigcup_{m\leq n} K_n$.

Let $p_n$ give a play by $P$. If $p$ is a cluster point of the $p_n$, then every open set about $p$ contains infinitely many $p_n$. Let $K_N$ be some compact neighborhood in $\{K_n : n<\omega\}$ which covers $p$. Then $K_N$ contains infinitely many $p_n$, which means sometime after round $N$, $P$ played in a set already covered by the strategy $\sigma$, which is an illegal move. Thus $\sigma$ is a winning predetermined strategy.
\end{proof}

\begin{cor}
The following are equivalent for a locally compact space $X$:
    \begin{itemize}
    \item $X$ is $\sigma$-compact
    \item $X$ is Lindel\"of
    \item $K \prewin G_{K,P}(X)$.
    \end{itemize}
\end{cor}

We now turn our attention to an example of a $\sigma$-compact space for which no predetermined strategy exists (which must, of course, not be locally compact). In fact, $P$ will instead have a winning tactical strategy.

\begin{defn}
Let $M=\omega^2\cup\{\infty\}$ denote the \textbf{metric fan space} with the topology generated by the singletons in $\omega^2$ and sets of the form $((\omega\setminus n)\times\omega) \cup \{\infty\}$ for $n<\omega$.
\end{defn}

\begin{prop}
For each compact set $C$ in $M$, there exists a minimal dominating function $f_C$ such that for each $(x,y)\in C\setminus\{\infty\}$, $f(x)> y$.
\end{prop}

\begin{lem}
$P \markwin G_{K,P}(M)$ where $M$ is the metric fan space. (This implies $K\not\uparrow G_{K,P}(M)$.)
\end{lem}

\begin{proof}
Let $P$ respond to the move $C\in K[X]$ by $K$ on round $n$ with the point $p=(n,s_C)$ such that $s_C = \min(\{y<\omega : f_C(n) < y\}$. It is easy to see that either $p_n\rightarrow \infty$, so $P$ has a winning tactical strategy.
\end{proof}

Furthermore, by a theorem due to Eric van Douwen...

\begin{thm}
Every first-countable non-locally countably compact space has the metric fan space $M$ as a closed subspace.
\end{thm}

... we have the following corollary:

\begin{cor}
$P \markwin G_{K,P}(X)$ where $X$ is a first-countable non-locally countably compact space. (This implies $K\not\uparrow G_{K,P}(X)$.)
\end{cor}

(Open question: does $P \tactwin G_{K,P}(X)$?)

\begin{thm}
$P \not\tactwin D_{K,P}(M)$ where $M$ is the metric fan space.
\end{thm}

\begin{proof}
Give $P$ the tactic $\sigma$. Suppose that for all $n<\omega$, there is an upper bound $m<\omega$ so that for each $C \in K[M]$, if $\pi_1(\sigma(C))=n$, then $\pi_2(\sigma(C))<m$. We may then define $f(n)=m$, and let $C_f=\{(x,y):f(x)<y\}\in K[M]$. $\sigma(C_f)$ must show a contradiction if $\sigma$ is legal.

So it follows that there is some $n<\omega$ such that there are compact sets $C_i\in K[M]$ with $\pi_1(\sigma(C_i))=n$ and $\pi_2(\sigma(C_i))<\pi_2(\sigma(C_{i+1}))$. The play $\left<C_0,\sigma(C_0),C_1,\sigma(C_1),\dots\right>$ is a counter to $\sigma$.
\end{proof}

While $K\prewin G_{K,P}(X)$ implies $X$ is $\sigma$-compact, it in fact implies something stronger.

\begin{defn}
A space $X$ is \textbf{hemicompact} if there exists a chain of increasing compact sets $K_0\subseteq K_1 \subseteq \dots$ such that every compact set in $X$ is a subset of some $K_n$.
\end{defn}

\begin{lem}
If $K\prewin G_{K,P}(X)$, then $X$ is hemicompact. Furthermore, any predetermined winning strategy for $K$ witnesses hemicompactness.
\end{lem}

\begin{proof}
Let $\sigma$ be a predetermined strategy for $K$ in the game $G_{K,P}(Y)$ such that there exists a compact set $C$ with $C \not\subseteq \sigma(n)$ for all $n$. On each turn, have $P$ play some $y_n\in C \setminus \sigma(n)$. Then the $y_n$ are an infinite subset of the compact set $C$ and must have a cluster point in $C$, showing $\sigma$ is not a winning strategy.

Thus if $K$ has a winning predetermined strategy, it witnesses that $Y$ is hemicompact.
\end{proof}

In fact, for locally compact spaces, finding winning predetermined strategies for $G_{K,P}(X)$ and $G_{K,L}(X)$ are equivalent problems.

\begin{thm}
The following are equivalent for any locally compact space $X$:
  \begin{itemize}
  \item $X$ is hemicompact.
  \item $K \prewin G_{K,L}(X)$.
  \item $K \prewin G_{K,P}(X)$.
  \end{itemize}
\end{thm}

\begin{proof}
Let $Y$ be hemicompact, witnessed by $K_n=\sigma(n)$. Let $L_0,L_1,\dots$ be a play by $L$ in $G_{K,L}(X)$. Suppose that this play defeats $\sigma$. Then let $x\in X$ be the point such that for all neighborhoods $U$ of $x$, $U$ hits infinite $L_n$. Let $C$ be a compact neighborhood of $x$, which must hit infinite $L_n$. As $K_n$ witnesses hemicompactness, $C \subseteq K_N = \sigma(N)$ for some $N$. But then $C\subset K_N$ intersects infinitely many $L_n$, which shows that the play $L_0,L_1,\dots$ was illegal. Thus $\sigma$ defeats every legal play by $L$ and is thus a winning predetermined strategy for $K$ in $G_{K,L}(X)$.

We conclude by noting that any winning strategy for $G_{K,L}(X)$ is a winning strategy for $G_{K,P}(X)$, and the existence of a winning predetermined strategy for $G_{K,P}(X)$ implies hemicompact by the previous lemma.
\end{proof}

\begin{cor}
The following are equivalent for any locally compact space $X$:
  \begin{itemize}
  \item $X$ is Lindel\"of.
  \item $X$ is $\sigma$-compact.
  \item $X$ is hemicompact.
  \item $K \prewin G_{K,L}(X)$.
  \item $K \prewin G_{K,P}(X)$.
  \end{itemize}
\end{cor}

The compact-point and compact-compact games are also useful in inspecting compactly generated ``k''-spaces.

\begin{defn}
A topological space is called a \textbf{$k$-space} if the following condition is satisfied: \[C \subseteq X \text{ is closed in } X\, \Leftrightarrow \, C\cap K \text{ is closed in } K \text{ for all compact sets } K\in K[X]\]
\end{defn}

\begin{defn}
A topological space is called a \textbf{$k_\omega$-space} if there exist $K_0,K_1,\dots \in K[X]$ that satisfy the following condition: \[C \subseteq X \text{ is closed in } X\, \Leftrightarrow \, C \cap K_n \text{ is closed in } K_n \text{ for all } n\]
\end{defn}

\begin{thm}
The following are equivalent for any Hausdorff $k$-space $X$:
  \begin{itemize}
  \item $X$ is hemicompact.
  \item $X$ is $k_{\omega}$.
  \item $K \prewin G_{K,P}(X)$.
  \end{itemize}
Furthermore, all predetermined strategies for $K$ witness hemicompact and $k_\omega$, and any witness to hemicompact/$k_\omega$ witnesses the other and serves as a predetermined strategy for $K$.
\end{thm}

\begin{proof}
If $X$ is hemicompact, then let it be witnessed by $K_n$. We claim $K_n$ also witnesses $k_\omega$. Note that the forward implication of $k_\omega$ always holds for $T_1$ spaces as $C\cap K_n$ is closed in $X$, and thus in every $K_n$. So assume $C\cap K_n$ is closed in $K_n$ for all $n$. Let $H$ be any compact set. As $X$ is hemicompact, $H\subseteq K_n$ for some $n$. Note $C\cap H = (C\cap K_n)\cap H$. As both $C \cap K_n$ and $H$ are closed in $K_n$, $C\cap H$ is closed in $K_n$, and thus $C\cap H$ is closed in $H$. As $Y$ is $k$ and $C\cap H$ is closed in $H$ for all compact $H$, $C$ is closed, showing the backwards implication.

Now if $Y$ is $k_\omega$, let it be witnessed by $K_n$. Give $K$ the predeterined strategy $\sigma(n)=K_n$ for the game $G_{K,P}(X)$, and let $p_n$ be the result of a legal counter by $P$. Suppose by way of contradiction that $p$ is a cluster point of the $p_n$. Note $p\in \sigma(N)$ for some $N$. $p$ is a cluster point of $\{p_n : n\geq N\}$ but $p\not\in \{p_n : n \geq N\}$. Also, $\{p_n : n \geq N\} \cap \sigma(m)$ is finite for all $m$, and thus closed, so as $\sigma(n)$ witnesses $k_\omega$, $\{p_n : n\geq N\}$ is closed and must contain its cluster point $p$, which is a contradiction. Thus $\sigma$ is a winning predetermined strategy for $K$ in $G_{K,P}(Y)$.

Finally, if $K \prewin G_{K,P}(X)$, $X$ is hemicompact by the previous lemma.
\end{proof}

For $k$-spaces, it turns out that finding winning predetermined strategies for $G_{K,P}(X)$ and $G_{K,L}(X)$ are also equivalent problems.

\begin{thm}
For any hemicompact Hausdorff $k$-space $X$, $K \prewin G_{K,L}(X)$.
\end{thm}

\begin{proof}
Let $X$'s hemicompactness be witnessed by $K_n=\sigma(n)$. Note that this also witnesses $k_\omega$ by the proof of the previous theorem. Let $H_0,H_1,\dots$ be a counter by $H$ for the game $G_{K,L}(X)$ in response to $\sigma$. Suppose by way of contradiction the counter was legal and defeats $\sigma$. Then there is a point $x$ such that every neighborhood of $x$ hits infinitely many of the $H_n$.

Now, $x\in\sigma(N)$ for some $N$, and since the play $H_0,H_1,\dots$ is legal, $x\not\in H_n$ for all $n\geq N$. Consider the set $H_\omega=\bigcup_{n\geq N} H_n$. Note that as the $K_n$ witness $k_\omega$, $H_\omega$ is closed if and only if $H_\omega \cap \sigma(m)$ is closed in $\sigma(m)$ for all $m$. In fact, since every $H_n$ is a subset of some $\sigma(m)$ (by hemicompactness), $H_\omega \cap \sigma(m)$ is a finite union of some $H_n$, and is thus closed in $Y$.

We thus have that $H_\omega$ is a closed set not containing $x$. But since every neighborhood of $x$ intersects $H_\omega$, $x$ is a limit point of the closed set $H_\omega$ and should be included, demonstrating our contradiction. Thus $\sigma$ is a winning predetermined strategy for $K$ in the game $G_{K,L}(X)$.
\end{proof}

\begin{cor}
The following are equivalent for any Hausdorff $k$-space $X$:
  \begin{itemize}
  \item $X$ is hemicompact.
  \item $X$ is $k_{\omega}$.
  \item $K$ has a winning predetermined strategy in $G_{K,L}(X)$.
  \item $K$ has a winning predetermined strategy in $G_{K,P}(X)$.
  \end{itemize}
\end{cor}

It's natural to question whethere there is ever any difference between finding winning predetermined strategies for $G_{K,P}(X)$ and $G_{K,L}(X)$. We now look to a (non-locally compact, non-$k$) Hausdorff space where the distinction arises:

\begin{defn}
Given a set $X$, an ultrafilter on $X$ is a collection $\mathcal{F}\subseteq\mathcal{P}(X)$ such that
    \begin{enumerate}
    \item $\emptyset\not\in \mathcal{F}$
    \item $A,B\in\mathcal{F} \Rightarrow A\cap B \in \mathcal{F}$
    \item $A\in\mathcal{F}$ and $A \subseteq B$ $\Rightarrow$ $B\in\mathcal{F}$
    \item $\forall A \subseteq X(A\in\mathcal{F}$ or $X\setminus A \in \mathcal{F})$
    \end{enumerate}
As a result, ultrafilters which contain a finite set contain only one singleton (and are called \textbf{principal}). Otherwise, ultrafilters which contain no finite sets are called \textbf{free}.
\end{defn}

\begin{defn}
The \textbf{Stone-Cech compactification} $\beta\omega$ of $\omega$ is the collection of ultrafilters on $\omega$. The principal ultrafilters containing a singleton $\{n\}$ are each identified with $n$ itself and are isolated. Free ultrafilters $\mathcal{F}$ are given neighborhoods of the form \[\{\mathcal{G} : \mathcal{G} \text{ is an ultrafilter on } \omega \text{ and } A \in \mathcal{G}\} = A \cup \{\mathcal{G}: \mathcal{G} \text{ is a free ultrafilter on } \omega \text{ and } A \in \mathcal{G}\}\] for each $A\in\mathcal{F}$.

Alternately $\beta\omega=\omega\cup\{\mathcal{F} : \mathcal{F}$ is a free ultrafilter on $\omega\}$ where $\omega$ is discrete and the free ultrafilters have the local base described above.
\end{defn}

\begin{defn}
A \textbf{single-ultrafilter space} is a subset of $\beta\omega$ containing all elements of $\omega$ and a single ultrafilter $\mathcal{F}$.
\end{defn}

\begin{prop}
The compact sets of a single-ultrafilter space are exactly the finite subsets of the space. Thus a single-ultrafilter space is neither locally compact nor $k$.
\end{prop}

Regardless of the ultrafilter chosen, we can see that $K$ has no hope of having a winning predetermined strategy for $G_{K,L}$ played on a single-ultrafilter space.

\begin{prop}
If $X$ is any single-ultrafilter space with the ultrafilter $\mathcal{F}$, then $K\not\prewin G_{K,L}(X)$.
\end{prop}

\begin{proof}
Compact sets are exactly finite sets in this space. Therefore, the difference of any two compact sets is compact.

Give $K$ the predetermined strategy $\sigma(n)$. $H$ counters with \[H_n=(n\cup\sigma(n+1))\setminus\sigma(n)\] on turn $n$. Since any free ultrafilter contains only unbounded sets, every neighborhood $A\cup\{\mathcal{F}\}$ of $\mathcal{F}$ must intersect infinitely many $H_n$, defeating $\sigma$.
\end{proof}

However, while it is consistant that there is an ultrafilter which defies the existance of a predetermined winning strategy for $K$ in $G_{K,P}$...

\begin{prop} 
If a selective ultrafilter $\mathcal{F}$ exists (this is independent of ZFC), then $K$ has no winning predetermined strategy in the compact-point game $G_{K,P}(Y)$ for the single selective ultrafilter space $Y=\omega \cup \{\mathcal{F}\}$.
\end{prop}

>>>>

\chapter{Proximal Game}

Results pertaining to Bell's proximal game for uniform spaces.

\section{cut-and-paste}

\begin{defn}
  A \textbf{uniform space} $\<X,\mc D\>$ is a set $X$ paired with a filter $\mc D$ (called its \textbf{uniformity}) of relations (called \textbf{entourages}) on $X$ such that for each entourage $D\in \mc D$:
    \begin{itemize}
      \item $D$ is reflexive, i.e., the diagonal $\Delta\subseteq D$.
      \item Its inverse $D^{-1}=\{\<y,x\>:\<x,y\>\in D\}\in \mc D$.
      \item There exists $\frac{1}{2}D\in\mc D$ such that 
        \[
          2(\frac{1}{2}D)=\frac{1}{2}D\circ\frac{1}{2}D=\{\<x,z\>:\exists y(\<x,y\>,\<y,z\>\in\frac{1}{2}D)\}\subseteq D
        \]
    \end{itemize}
  Note that since $\mc D$ is a filter, for each $D\in\mc D$, the symmetric relation $D\cap D^{-1}\in \mc D$.
\end{defn}

\begin{prop}
For each $D\in\mc D$ and $n<\omega$ there exists $\frac{1}{2^{n+1}}D\in\mc D$ such that 
  \[2(\frac{1}{2^{n+1}}D)=\frac{1}{2^{n+1}}D\circ \frac{1}{2^{n+1}}D\subseteq \frac{1}{2^{n}}D\]
and if $2E\subseteq \frac{1}{2^{n}}D$, then $E\subseteq \frac{1}{2^{n+1}}D$.
\end{prop}

\begin{defn}
  For an entourage $D\in\mc D$, let $D[x]=\{y:(x,y)\in D\}$ be the \textbf{$D$-neighborhood} of $x$. The \text{uniform topology} for a uniform space $\<X,\mc D\>$ is generated by the base $\{D[x]:x\in X,D\in\mc D\}$.
\end{defn}

\begin{thm}
  A space $X$ is uniformizable (its topology is the uniform topology for some uniformity) if and only if $X$ is completely regular ($T_{3\frac{1}{2}}$).
\end{thm}

\begin{prop}
  If $X$ is a uniform space, then for all $x\in X$ and symmetric entourages $D$:
    \[
      x\in \frac{1}{2}D[y]\text{ and } y\in\frac{1}{2}D[z] \Rightarrow x\in D[z]
    \]
  and
    \[
      \frac{1}{2}D[x]\subseteq \cl{\frac{1}{2}D[x]}\subseteq D[x]
    \]
\end{prop}

\begin{proof}
  The first is by definition of $\frac{1}{2}D$.

  If $z\in \cl{\frac{1}{2}D[x]}$, it follows that there is $y\in \frac{1}{2}D[x]\cap\frac{1}{2}D[z]$ since $\frac{1}{2}D[z]$ is an open neighborhood of $z$. Thus $(x,z)\in D \Rightarrow z\in D[x] \Rightarrow \cl{\frac{1}{2}D[x]}\subseteq D[x]$.
\end{proof}

\begin{defn}
  For a uniform space $X$, Bell's proximity game proceeds as follows.

  In round $0$, $\pl D$ chooses an entourage $D_0$, followed by $\pl P$ choosing a point $p_0\in X$.

  In round $n+1$, $\pl D$ chooses an entourage $D_{n+1}\subseteq D_n$, followed by $\pl P$ choosing a point $p_{n+1}\in 4D_n[p_n]$.

  Player $\pl D$ wins if either $\bigcap_{n<\omega} 4D_n[p_n] = \emptyset$ or $\<p_0,p_1,\dots\>$ converges.
\end{defn}

\begin{defn}
  For a uniform space $X$, the simplified proximal game $\proxgame{X}$ can be defined as follows:

  In round $0$, $\pl D$ chooses a symmetric entourage $D_0$, followed by $\pl P$ choosing a point $p_0\in X$.

  In round $n+1$, $\pl D$ chooses a symmetric entourage $D_{n+1}$, followed by $\pl P$ choosing a point $p_{n+1}\in\left(\bigcap_{m\leq n}D_m\right)[p_n]$.

  Player $\pl D$ wins if either $\bigcap_{n<\omega}\left(\bigcap_{m\leq n} D_m\right)[p_n]=\emptyset$ or $\<p_0,p_1,\dots\>$ converges.
\end{defn}

\begin{thm}
  $\pl D$ has a winning perfect-information strategy in Bell's game if and only if $\pl D\win\proxgame{X}$.
\end{thm}

\begin{proof}
  Let $\sigma$ be a winning perfect information strategy for $\pl D$ in Bell's game. We define a perfect information strategy $\tau$ in the simplified game to yield symmetric entourages $\tau(p\rest n)=\sigma(p\rest n)\cap(\sigma(p\rest n))^{-1}$ for all partial attacks $p\rest n$. Note that $\tau(p\rest n)=\bigcap_{m\leq n}\tau(p\rest m)$.

  If $p$ attacks $\tau$ in the simplified game, $p(n+1)\in\left(\bigcap_{m\leq n}\tau(p\rest m)\right)[p(n)]=\tau(p\rest n)[p(n)]\subseteq\sigma(p\rest n)[p(n)]\subseteq 4\sigma(p\rest n)[p(n)]$, so $p$ attacks $\sigma$ in Bell's game. Thus either $p$ converges, or 
    \[
      \emptyset
        =
      \bigcap_{n<\omega} 4\sigma(p\rest n)[p(n)]
        \supseteq 
      \bigcap_{n<\omega}\tau(p\rest n)[p(n)]
        =
      \bigcap_{n<\omega}\left(\bigcap_{m\leq n}\tau(p\rest n)\right)[p(n)]
    \]

  For the other direction, let $\sigma$ be a winning perfect information strategy for $\pl D$ in the simplified game such that $\sigma(p\rest n)=\bigcap_{m\leq n}\sigma(p\rest m)$. Define the perfect information strategy $\tau$ in Bell's Game such that $4\tau(p\rest n)\subseteq \sigma(p\rest n)$ and $\tau(p\rest n)=\bigcap_{m\leq n}\tau(p\rest m)$ for all partial attacks $p\rest n$.

  If $p$ attacks $\tau$ in Bell's game, $p(n)\in 4\tau(p\rest n)\subseteq\sigma(p\rest n)=\bigcap_{m\leq n}\sigma(p\rest m)$, so $p$ attacks $\sigma$ in the simplified game. Thus either $p$ converges, or
    \[
      \emptyset
        =
      \bigcap_{n<\omega}\left(\bigcap_{m\leq n}\sigma(p\rest n)\right)[p(n)]
        =
      \bigcap_{n<\omega}\sigma(p\rest n)[p(n)]
        \supseteq
      \bigcap_{n<\omega}4\tau(p\rest n)[p(n)]
        \supseteq
      \bigcap_{n<\omega}\tau(p\rest n)[p(n)]
    \]
\end{proof}

\begin{prop}
$\pl P$ has a winning perfect-information strategy in Bell's game if and only if $\pl P \win \proxgame{X}$.
\end{prop}

\begin{proof}
  Similar to the previous.
\end{proof}

\begin{defn}
  A uniform space is \textbf{proximal} if $\pl D \win \proxgame{X}$.
\end{defn}

\begin{defn}
  For a space $X$ and a point $x\in X$, the \textbf{$W$-convergence-game} $\congame{X}{x}$ proceeds as follows.

  In round $0$, $\pl O$ chooses a neighborhood $U_n$ of $x$, followed by $\pl P$ choosing a point $p_n\in \bigcap_{m\leq n}U_m$.

  Player $\pl O$ wins if $\<p_0,p_1,\dots\>$ converges.
\end{defn}

\begin{defn}
  A space is \textbf{$W$} if $\pl O \win \congame{X}{x}$ for all $x\in X$.
\end{defn}

\begin{defn}
  For each finite tuple $(m_0,\dots,m_{n-1})$, we define the \textbf{$k$-tactical fog-of-war}
    \[
      T_k(\<m_0,\dots,m_{n-1}\>)=\<m_{n-k},\dots,m_{n-1}\>
    \]
  and the \textbf{$k$-Mark\"ov fog-of-war}
    \[
      M_k(\<m_0,\dots,m_{n-1}\>)=\<\<m_{n-k},\dots,m_{n-1}\>,n\>
    \]

  So $P\ktactwin{k}G$ if and only if there exists a winning strategy for $P$ of the form $\sigma\circ T_k$, and $P\kmarkwin{k}G$ if and only if there exists a winning strategy of the form $\sigma\circ M_k$.
\end{defn}

\begin{thm}
For all $x\in X$:
  \begin{itemize}
    \item
      $\pl D\win \proxgame{X} \Rightarrow \pl O \win \congame{X}{x}$
    \item
      $\pl D\ktactwin{2k} \proxgame{X} \Rightarrow \pl O \ktactwin{k} \congame{X}{x}$
    \item
      $\pl D\kmarkwin{2k} \proxgame{X} \Rightarrow \pl O \kmarkwin{k} \congame{X}{x}$
  \end{itemize}
\end{thm}

\begin{proof}
Let $\sigma$ witness $\pl D \ktactwin{2k}\proxgame{X}$ (resp. $\pl D \kmarkwin{2k}\proxgame{X}$, $\pl D\win\proxgame{X}$). We define the $k$-tactical (resp. $k$-Mark\"ov, perfect info) strategy $\tau$ such that
  \[
    \tau\circ L_k(p)
      =
    \sigma\circ L_{2k}(\<x,p(0),\dots,x,p(|p|-1)\>)[x]
      \cap
    \sigma\circ L_{2k}(\<x,p(0),\dots,x,p(|p|-1),x\>)[x]
  \]
where $L_{2k}$ is the $2k$-tactical fog-of-war (resp. $2k$-Mark\"ov fog-of-war, identity) and $L_{k}$ is the $k$-tactical fog-of-war (resp. $k$-Mark\"ov fog-of-war, identity).

Let $p$ attack $\tau$. Consider the attack $q$ against the winning strategy $\sigma$ such that $q(2n)=x$ and $q(2n+1)=p(n)$, and let $D_n=\sigma\circ L_{2k}(q)$ and $E_n=\bigcap_{m\leq n}D_n$.

Certainly, $x\in E_{2n}[x]= E_{2n}[q(2n)]$ for any $n<\omega$. Note also for any $n<\omega$ that 
    \[
      p(n) \in 
      \bigcap_{m\leq n}\tau\circ L_k(p\rest n)
    \]
    \[
      =
      \bigcap_{m\leq n}\left(
        \sigma\circ L_{2k}(\<x,p(0),\dots,x,p(m-1)\>)[x]\cap
        \sigma\circ L_{2k}(\<x,p(0),\dots,x,p(m-1),x\>)[x]
      \right)
    \]
    \[
      =
      \bigcap_{m\leq n}\left(
        D_{2m}[x]\cap
        D_{2m+1}[x]
      \right) =
      \bigcap_{m\leq 2n+1} D_m[x]=E_{2n+1}[x]
    \]
so by the symmetry of $E_{2n+1}$, $x\in E_{2n+1}[p(n)]= E_{2n+1}[q(2n+1)]$. Thus $x\in \bigcap_{n<\omega} E_n[q(n)]\not=\emptyset$, and since $\sigma$ is a winning strategy, the attack $q$ converges. Since $q(2n)=x$, $q$ must converge to $x$. Thus its subsequence $p$ converges to $x$, and $\tau$ is a winning strategy in $\congame{X}{x}$.
\end{proof}

\begin{cor}
For all $x\in X$:
  \begin{itemize}
    \item
      $\pl D\ktactwin{k} \proxgame{X} \Rightarrow \pl O \ktactwin{k} \congame{X}{x}$
    \item
      $\pl D\kmarkwin{k} \proxgame{X} \Rightarrow \pl O \kmarkwin{k} \congame{X}{x}$
  \end{itemize}
\end{cor}

\begin{cor}
  All proximal spaces are $W$-spaces.
\end{cor}

\begin{thm}
  Let $X\cup\{\infty\}$ be a uniformizable space such that $X$ is discrete. Then
  \begin{itemize}
    \item
      $\pl O\win \congame{X\cup\{\infty\}}{\infty} \Rightarrow \pl D \win \proxgame{X\cup\{\infty\}}$
    \item
      $\pl O\ktactwin{k} \congame{X\cup\{\infty\}}{\infty} \Rightarrow \pl D \ktactwin{k} \proxgame{X\cup\{\infty\}}$
    \item
      $\pl O\kmarkwin{k} \congame{X\cup\{\infty\}}{\infty} \Rightarrow \pl D \kmarkwin{k} \proxgame{X\cup\{\infty\}}$
  \end{itemize}
\end{thm}

\begin{proof}
  Note that the topology on $X\cup\{\infty\}$ is induced by the uniformity with equivalence relation entourages $D(U)=\Delta\cup U^2$ for each open neighborhood $U$ of $\infty$.

  Let $\sigma$ witness $\pl D \ktactwin{k}\congame{X\cap\{\infty\}}{\infty}$ (resp. $\pl D \kmarkwin{k}\congame{X\cap\{\infty\}}{\infty}$, $\pl D\win\congame{X\cap\{\infty\}}{\infty}$). We define the $k$-tactical (resp. $k$-Mark\"ov, perfect info) strategy $\tau$ such that
    \[
      \tau\circ L(p)
        =
      D(\sigma\circ L(p))
    \]
  where $L$ is the $k$-tactical fog-of-war (resp. $k$-Mark\"ov fog-of-war, identity).

  Let $p\in (X\cup\{\infty\})^\omega$ attack $\tau$ such that $\bigcap_{n<\omega}\tau(p\rest n)[p(n)]\not=\emptyset$.

  If $\infty\in\bigcap_{n<\omega}\tau(p\rest n)[p(n)]$, it follows that $p$ is an attack on $\sigma$. Since $\sigma$ is a winning strategy, it follows that $q$ and its subsequence $p$ must coverge to $\infty$.

  Otherwise, $\infty\not\in\tau(p\rest N)[p(N)]$ for some $N<\omega$, and then $\tau(p\rest N)[p(N)]=\{p(N)\}$ implies $p\to p(N)$.

  Thus $\tau\circ L$ is a winning strategy.
\end{proof}

\begin{cor}
  Let $X\cup\{\infty\}$ be a uniformizable space such that $X$ is discrete. Then
  \begin{itemize}
    \item
      $\pl O\win \congame{X\cup\{\infty\}}{\infty} \Leftrightarrow \pl D \win \proxgame{X\cup\{\infty\}}$
    \item
      $\pl O\ktactwin{k} \congame{X\cup\{\infty\}}{\infty} \Leftrightarrow \pl D \ktactwin{k} \proxgame{X\cup\{\infty\}}$
    \item
      $\pl O\kmarkwin{k} \congame{X\cup\{\infty\}}{\infty} \Leftrightarrow \pl D \kmarkwin{k} \proxgame{X\cup\{\infty\}}$
  \end{itemize}
\end{cor}

\begin{prop} For any $x\in X$ and $k\geq 1$,
  \begin{itemize}
    \item
      $\pl O\ktactwin{k}\congame{X}{x} \Leftrightarrow \pl O\tactwin\congame{X}{x}$
    \item
      $\pl O\kmarkwin{k}\congame{X}{x} \Leftrightarrow \pl O\markwin\congame{X}{x}$
  \end{itemize}
\end{prop}

\begin{proof}
  If $\sigma$ witnesses $\pl O\ktactwin{k}\congame{X}{x}$, let $\tau(\emptyset)=\sigma(\emptyset)$ and
    \[
      \tau(\<q\>)
        =
      \bigcap_{i< k}
      \sigma(\<\underbrace{x,\dots,x}_{k-i-1},q,\underbrace{x,\dots,x}_{i}\>)
    \]

  This is easily verified to be a winning strategy. The proof for $\pl O\kmarkwin{k}\congame{X}{x}$ is analogous.
\end{proof}

\begin{cor}
  Let $X\cup\{\infty\}$ be a uniformizable space such that $X$ is discrete, and $k\geq 1$. Then
  \begin{itemize}
    \item
      $\pl D\ktactwin{k}\proxgame{X\cup\{\infty\}} \Leftrightarrow O\tactwin\proxgame{X\cup\{\infty\}}$
    \item
      $\pl D\kmarkwin{k}\proxgame{X\cup\{\infty\}} \Leftrightarrow O\markwin\proxgame{X\cup\{\infty\}}$
  \end{itemize}
\end{cor}

\begin{prop} For any uniform space $X$,
  \begin{itemize}
    \item
      $\pl O\ktactwin{k}\proxgame{X} \Leftrightarrow \pl O\ktactwin{2}\proxgame{X}$
    \item
      $\pl O\kmarkwin{k}\proxgame{X} \Leftrightarrow \pl O\kmarkwin{2}\proxgame{X}$
  \end{itemize}
\end{prop}

\begin{proof}
  If $\sigma$ witnesses $\pl O\ktactwin{k}\congame{X}{x}$, let $\tau(\emptyset)=\sigma(\emptyset)$ and
    \[
      \tau(\<q\>)
        =
      \bigcap_{i<k}
      \sigma(\<\underbrace{q,\dots,q}_{i}\>)
    \]
    \[
      \tau(\<q,q'\>)
        =
      \bigcap_{i< k}
      \sigma(\<\underbrace{q,\dots,q}_{k-i},\underbrace{q',\dots,q'}_{i}\>)
    \]

  This is easily verified to be a winning strategy. The proof for $\pl O\kmarkwin{k}\congame{X}{x}$ is analogous.
\end{proof}

\newpage

\begin{defn}
  The absolute proximal game $\aproxgame{X}$ is analogous to $\proxgame{X}$, except $\pl D$ may only win if $p$ converges.
\end{defn}

\begin{defn}
  A \textbf{uniformly locally compact} space is a uniformizable space with a \textbf{uniformly compact entourage} $M$ where $\cl{M[x]}$ is compact for all $x$.
\end{defn}

\begin{thm}
  For any uniformly locally compact space $X$,
      $\pl D\win \proxgame{X} \Leftrightarrow \pl D\win \aproxgame{X}$
\end{thm}
